---
title: "simpleRegress"
author: "Kevin Brandon Salazar"
date: "Summer 2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## make a simple regression model

```{r}
bears <- read.csv(file="BEARS.csv",header = TRUE)
#adjust factors to be factors
bears$SEX<- as.factor(bears$SEX)
bears$MONTH<- as.factor(bears$MONTH)
```

## Model LENGTH ~ NECK  this is an example  

We are to compute regression models finding one regression model that does the best job in predicting the bear length and its correspondence to the bears neck size, age head weight and head length.

```{r}
simp <- lm(LENGTH~NECK,data=bears)
plot(LENGTH~NECK,data=bears)
abline(simp)
summary.lm(simp)
```
The adjusted r square that is the largest is the best. For the neck size is 0.7476 

## Compare all models that predict LENGTH other than NECK. Then order them from worst to best by its value of Adjusted-Rsquared (bigger is better), or by RSE (residual standard error) where smaller is better. 

```{r}
simp <- lm(LENGTH~HEADLEN,data=bears)
plot(LENGTH~HEADLEN,data=bears)
abline(simp)
summary.lm(simp)
```

The adjusted r square for head length is 0.8483

```{r}
simp <- lm(LENGTH~HEADWTH,data=bears)
plot(LENGTH~HEADWTH,data=bears)
abline(simp)
summary.lm(simp)
```

The adjusted r square for head width is 0.5321

```{r}
simp <- lm(LENGTH~AGE,data=bears)
plot(LENGTH~AGE,data=bears)
abline(simp)
summary.lm(simp)
```

The adjusted r square for age is 0.5073

```{r}
simp <- lm(LENGTH~CHEST,data=bears)
plot(LENGTH~CHEST,data=bears)
abline(simp)
summary.lm(simp)
```

The adjusted r square for CHEST is 0.7869

```{r}
simp <- lm(LENGTH~WEIGHT,data=bears)
plot(LENGTH~WEIGHT,data=bears)
abline(simp)
summary.lm(simp)
```

The adjusted r square for weight is 0.7423

## Conclusion/Discussion
In conclusion the main question at hand that we've answered today is which regression model that does the best job in predicting the bear length and its correspondence to the bears neck size, age head weight and head length? After conducting multiple tests and have figured out the worse (lowest) to best which is (highest). So starting with lowest it is age (0.5073), head width (0.5321), weight (0.7423), CHEST (0.7869), head length (0.8483). Therefore after running these tests based of the results that we've received we can conclude that the best one is head length since it has the largest r square value.